A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-11 JTB_supp/JTB_supp.Rmd
rerun Fig S9 from 1-60

# Set input values for steady state runs
input <- expand.grid(L=seq(10,55,1), initS=c(0.0001,0.1))

@@

```{r plotFigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F}
# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1))

>>>>

# Set input values for steady state runs
input <- expand.grid(L=seq(1,60,1), initS=c(0.0001,0.1))

@@

```{r plotFigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F}
# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1), mgp=c(1.5,0.5,0), tcl=-0.025)
